%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[letterpaper,twocolumn,10pt]{article}
\input{tex/usepackage}
\input{tex/custom}
\input{src/acronyms}
\microtypecontext{spacing=nonfrench}
%-------------------------------------------------------------------------------
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newenvironment{todoenv}{\color{red}}{\ignorespacesafterend}
\newcommand{\NAME}{\textcolor{red}{LanDscAPe}}
% can be used to comment out text
\newcommand{\mycomment}[1]{}
\usepackage{pdflscape}
\begin{document}
\section{LDAP Passwords}
% This would be great for the Disclosure!
%LDAP is an application protocol that facilitates central user administration and can be used with various directory services. These directory services (e.g., Microsoft Active Directory) store user and account information as well as security information such as passwords (https://learn.microsoft.com/de-de/entra/architecture/auth-ldap) to facilitate single sign-on. For this reason, LDAP is often used as a central component of many single sign-on systems. 

%Most LDAP servers implement a streamlined login mechanism, allowing users to simply enter their username and password. The login process typically unfolds as follows: Initially, a search operation is initiated for the provided username. This necessitates that LDAP servers permit unauthenticated searches, a configuration found in a majority of servers \todo{(x\%)}. Absent this permission, user sign-in becomes cumbersome, necessitating the user's knowledge of their Distinguished Name (DN), such as \texttt{CN=John Doe, OU=Users, DC=example, DC=com}. 

%Upon successfully locating the user through the search, the system proceeds to bind using the retrieved DN and the provided password. It is imperative that the password remains confidential, known only to the respective user. However, our investigation has unearthed two significant vulnerabilities in this process. Firstly, the original RFC4519 \todo{\cite{}} stipulates that passwords are not stored in an encrypted or hashed format. Secondly, we have observed instances of server misconfiguration by administrators, leading to passwords being accessible to unauthorized individuals. Our findings include the discovery of \todo{x} plaintext passwords across \todo{y} servers, offering profound insights which we elaborate on in this chapter. 
Since authentication using \gls{LDAP} without a service account requires unauthenticated search access, special care must be taken so that confidential data is not leaked to unauthenticated attackers.

\subsection{Part 1: Secret Leaking Attributes}

Table \todo{~\cref{tab:UserPasswordSupport}} indicates that a substantial proportion, \todo{y\%}, of LDAP servers support the \texttt{userPassword} attribute. This attribute, as defined in the OpenLDAP Documentation and aligned with RFC4519, is specifically designated for storing passwords.

Furthermore, as demonstrated by Table \todo{~\cref{tab:UserPasswordProvision}}, \todo{x\%} of these servers actually expose the \texttt{userPassword} attribute. This is particularly concerning considering the RFC specification, which suggests that sensitive information, such as plaintext passwords, might be stored in this attribute and could potentially be accessed without requiring authentication.

Prior to delving deeper into this hypothesis, we considered the possibility of alternative attributes being utilized for storing secrets, which might not be as readily apparent. To explore this, we constructed three comprehensive lists of LDAP attributes and systematically cross-referenced them. This meticulous approach yielded a compilation of LDAP attributes commonly used for credential storage \todo{(detailed in the Appendix)}.

Armed with this refined list of attributes, we proceeded to ascertain the prevalence of servers promoting any of these attributes, as well as the number of LDAP object instances containing these attributes. The culmination of our findings is succinctly presented in Table \todo{~\cref{tab:AdditionalSecretAttributes}}.

\subsection{Attribute Content Evaluation}

Knowing that servers might expose secrets, we dived deeper into our dataset, evaluating the content of the attributes. We asked ourselves the question, are there really plain text passwords or secret tokens publicly available, or is the data possibly probably censored and actually not accessible after all?

\subsubsection{The OpenLDAP userPassword Field}

The starting point for our evaluation was the OpenLDAP documentation, which recommends storing passwords in a hashed format within the \texttt{userpassword} attribute and defines the following storage scheme for this purpose \cite{}:

\begin{itemize}
    \item \textbf{SSHA Password Storage Scheme:} The SSHA (Salted SHA) password storage scheme is a salted version of the SHA algorithm and is considered one of the most secure methods. It adds a unique salt to each password before hashing, enhancing security against precomputed rainbow table attacks. For example, the following values represent the same password in different salted forms: 

    \begin{verbatim}
    {SSHA}DkMTwBl+a/3DQTxCYEApdUtNXGgdUac3
    {SSHA}d0Q0626PSH9VUld7yWpR0k6BlpQmtczb
    \end{verbatim}
    
    \item \textbf{CRYPT Password Storage Scheme:} This scheme leverages the operating system's \texttt{crypt(3)} hash function, capable of supporting a variety of hashing algorithms. The resultant hashed value is prefixed with a dollar sign and an identifier (\$<id>), where <id> denotes the specific hashing algorithm used—'1' for MD5, '8' for PBKDF2, and so on. For instance, a \texttt{userPassword} attribute's crypt value could appear as follows:

    \begin{verbatim}
    {CRYPT}$1$czBJdDqS$TmkzUAb836oMxg/BmIwN.1
    \end{verbatim}

    \item \textbf{MD5 Password Storage Scheme:} Hashing the password using the MD5 algorithm is widely regarded as insecure in modern cryptographic practices.

    \item \textbf{SMD5 Password Storage Scheme:} This scheme represents an advancement over the standard MD5 algorithm by incorporating salt into the hashing process. This addition results in the potential for multiple unique hash representations for the same password. Example representations are as follows:

    \begin{verbatim}
    {SMD5}4QWGWZpj9GCmfuqEvm8HtZhZS6E=
    {SMD5}g2/J/7D5EO6+oPdklp5p8YtNFk4=
    \end{verbatim}
    
\end{itemize}

This methodology enabled us to conduct a content evaluation predicated on a pattern that identifies the tag of the stored value. However, considering that merely x servers were identified as OpenLDAP servers (refer to Chapter~\ref{chapter:OpenLDAPServers}), and not every OpenLDAP administrator adheres strictly to the configuration guidelines outlined in the official documentation, it became imperative to broaden the scope of our evaluation.

\subsubsection{NTLM Hashes}

A common secret combination we encountered involved the NT password hash and the LM password hash, stored in the attributes \texttt{sambaNTPassword} and \texttt{sambaLMPassword}, respectively. When both an NT password hash and an LM (LAN Manager) password hash are present, they represent distinct secrets. Below is a concise elucidation of each:

\begin{itemize}
    \item \textbf{NT Password Hash:} Utilized by more contemporary versions of Windows (initiating with Windows NT), this hash type offers enhanced security. It is generated by applying the MD4 hashing algorithm to the Unicode (UTF-16LE) encoded version of the password.
    
    \item \textbf{LM Password Hash:} An archaic and less secure hash format, predominantly used by legacy systems (like Windows 95/98 and early versions of Windows NT). LM hashes are infamously weak due to their methodology: they convert the password to uppercase, pad it to 14 characters, divide it into two 7-character segments, and then hash each segment using the DES algorithm.
    
    \item \textbf{NTLM:} NTLM (NT LAN Manager) is an authentication protocol that can utilize either of these hash types for authentication, contingent on the system configuration. NTLM represents a suite of protocols superseding the original LAN Manager authentication. NTLMv1 primarily employed LM hashes, whereas NTLMv2, noted for its heightened security, utilizes NT hashes.
\end{itemize}

\subsubsection{AD and Kerberos Principal Key}

\todo{write}

\subsubsection{Password Evaluation}

During our research, we further refined our password evaluation, incorporating various additional criteria beyond those presented in sections \ref{subsubsec:OpenLDAPuserPassword} and \ref{subsubsec: SambaNTLMHashes} Our final process for assessing the content of a password field can be systematically explained as follows:

\begin{enumerate}
    \item Identification of redacted passwords: Some passwords are indeed censored, meaning their actual value remains undisclosed. The redaction typically appears as: ******** or \#\#\#\#\#\#\#\#\#.
    \item Identification of NTLM hashes: The field names were significantly useful for identifying these values. Random sampling demonstrated that certain fields, such as \texttt{sambalmpassword} and \texttt{sambantpassword}, contain NTLM hashes.
    \item Identification by tag: Many hash values can be identified by their tag. For instance, according to OpenLDAP documentation, passwords are stored in the format \{TAG\}Value. The various tags are described in section x.y.z.
    \item Identification of potential hash values: Certain hash formats, like BCRYPT or MD5, have specific characteristics. For example, the BCRYPT format has a rather distinct pattern, and an MD5 hash always has a fixed length of 32 bytes.
    \item Identification of encoded values: Recognizable again by patterns. For example, due to padding, 2/3 of Base64 encoded values end with one or two '=' characters. Decoding is tentatively performed, and the result or error is analyzed to determine if it represents an encoded value. Some values also explicitly indicate their encoding method.
\end{enumerate}

This procedure significantly reduced the number of values. However, a set of x values remained. Subsequently, we conducted a manual evaluation of samples, confirming that the majority of the remaining values consisted primarily of passwords in plaintext. 

Adding to that, we categorized them as plaintext passwords, acknowledging that a small fraction of this classification might be incorrect. However, we lack any alternative method to automate this process, as manually verifying each server would be prohibitively expensive. In Section \ref{}, however, we examine these plaintext passwords more closely and carry out validity checks.

In total, Y servers were found populating password fields, and detailed results of our content evaluation  is presented in Table X. This table shows that X servers transmit Y (Y\%) secrets in an insecure format and of these V (V\%) shockingly even plaintext passwords.

\subsection{Plaintext Entropie Evaluation}

With the knowledge that certain servers expose plaintext passwords, we still asked ourselves whether these were test servers for demonstration purposes, if they contained real cleartext credentials from actual users, and if so, how many? To answer these questions, we decided to calculate the entropy of these values as follows:

The entropy \( E(X) \) of a set of passwords can be calculated using the formula below, where \( c_{ij} \) represents the character \( i \) of password \( j \):

\[
E(X) = \frac{1}{ml(pw)} \sum_{i=1}^{ml(pw)} -\sum_{j=1}^{l(c_i)} P(c_{ij}) \log_2 P(c_{ij})
\]

In this formula, \( ml(pw) \) represents the maximum length of all passwords in the set, \( l(c_i) \) is the number of occurrences of character \( i \) in all passwords, and \( P(c_{ij}) \) is the probability of character \( i \) being in position \( j \) in any given password.

This formula allows us to measure the randomness of password values. Our assumption is that cleartext passwords on demo servers exhibit relatively low entropy, while cleartext passwords on real servers demonstrate relatively high entropy. This assumption is grounded in common password practices and the differing priorities associated with demo versus real server environments. In demo server settings, there is often a tendency to use simplistic or repetitive passwords, as the primary focus is on ease of access and demonstration rather than on security. The password variety is not a priority, and it is not uncommon for demo servers to employ a uniform or a limited set of passwords across multiple accounts. This practice naturally results in lower entropy, indicating less complexity and randomness in password composition. In contrast, real servers are typically subjected to stringent security protocols and password policies. These policies often enforce the creation of complex passwords that include a mix of letters, numbers, and special characters, aimed at enhancing security. Users of real servers are also more likely to be mindful of password strength, given the real and often critical data protected by these passwords. Consequently, the password entropy in real servers tends to be higher, reflecting a greater level of randomness and unpredictability, in line with stronger security measures.

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Server Type} & \textbf{User} & \textbf{Password} \\ \midrule
\textbf{Demo Server (A)} & admin         & admin             \\
                         & test1         & test1             \\
                         & test2         & test2             \\
                         & test3         & test3             \\ \midrule
\textbf{Real Server (B)} & admin         & kil2z@            \\
                         & ralph         & siz1:a!           \\
                         & nick          & az33x>l           \\
                         & marie         & marie123          \\ \bottomrule
\end{tabular}
\caption{Comparison of User-Password Pairs from Demo and Real Servers}
\end{table}

Calculating the entropy for these servers shows that the demo server has a fairly low entropy of x compared to the user password server, which as a fairly high entropy of Y. Of course, this approach comes with some limitations, including:

\begin{itemize}
    \item The method assumes independence between passwords, which may not hold in practice.
    \item The sample sizes are different, small due to our limitation for ethical reasons and in a few cases (e.g. server size limit of 3) too small to actually make reliable statements.
    \item It may not accurately reflect human behavior in choosing passwords.
\end{itemize}

However, it allowed us to automatically determine servers that are more likely to contain real password examples.

\subsubsection{Statistical Insights on Entropy:}

Our comprehensive analysis of plain text password entropy across LDAP servers yielded significant insights, indicative of varying security postures. The key findings are summarized as follows:

\begin{enumerate}
    \item \textbf{Minimum Entropy:} The lowest entropy value recorded was \todo{0}, suggesting complete predictability or lack of randomness in certain passwords.
    \item \textbf{Maximum Entropy:} Conversely, the highest entropy observed was \todo{5.82}, implying robust password complexity in some instances.
    \item \textbf{Average Entropy:} The mean entropy across the sampled passwords was found to be \todo{1.53}, indicating a generally low level of randomness and complexity.
\end{enumerate}

Totaling \todo{X} server, exhibited a password entropy of 0. This denotes an absolute absence of randomness. Our analysis, grounded in a random sampling methodology, attributes this phenomenon to several factors:

\begin{itemize}
    \item Instances where only a single password sample was available, making entropy an unreliable metric.
    \item Usage of the same password across multiple test users, typically observed in demo or test servers.
\end{itemize}

Considering that X servers exhibited a multitude of password samples yet consistently demonstrated an entropy value of 0, we deduced that these servers are likely employed for demonstration or testing purposes.

Additionally, we observed 252 servers with entropy values less than or equal to 1, denoting minimal randomness. Further investigation into a random subset of these servers revealed:

\begin{itemize}
    \item Predominance of test or demo servers, where a common set of test passwords is used with minor variations.
    \item Presence of predictable password scheme, such as a concatenation of an organization name and a four-digit PIN.
\end{itemize}

Conversely, \todo{Y} servers demonstrated entropy values above 1, indicative of higher randomness. We discovered through random sampling that this pattern is commonly associated with legitimate, operational servers exposing plaintext passwords of users. 

To gauge the extent of the issue, we embarked on a quantitative analysis by counting the number of user entries with associated passwords on the X servers. This approach provided us with a clear indicator of how many users were potentially affected by the security oversight.

In conducting our research, we have set ourselves strict ethical rules, including that we only count passwords without having them sent to us. We accomplished this by conducting a recursive search with an asterisk similar to the brute-force algorithm detailed in Chapter \todo{X}. This was coupled with a condition that verified the presence of a password field (refer to \todo{ref}). In addition, we crafted our server requests to exclusively solicit the Distinguished Name (DN) and ObjectClasses, ensuring minimal data retrieval without sensitive information. While the DN is invariably obtained, the inclusion of ObjectClasses in our responses was instrumental. It provided us with the necessary insight into the object types predominantly susceptible to this issue, thereby assisting in the identification of broader patterns and regularities.

The graph (refer to Graph~\ref{fig:graphX}) illustrates the distribution of affected users (denoted as $x$) across $y$ servers, characterized by an entropy measure of $z$. Notably, a significant number of users---specifically, \todo{INSERT NUMBER}---have had their passwords exposed with an entropy level exceeding 1. This situation is particularly concerning as it includes the passwords of system administrators, thereby presenting criminals with potential avenues for further system exploitation. Moreover, the risk is compounded by the prevalent issue of password reuse \todo{ADD CITATION}. This could potentially compromise other applications used by the affected individuals, leading, for example, to unauthorized access to personal accounts on platforms such as Twitter and Instagram. This makes social engineering attacks possible, for example. This domino effect amplifies the potential for damage, extending the impact of this exposure far beyond the initially compromised server.

\subsection{Part 4: Biggest Findings and Examples}

\todo{write}

\subsubsection{Ethical Considerations concerning password research.}

\todo{write}

\todo{insert values}

\todo{What about SASL and Kerberos???}

\todo{let Fabian proofread}


\subsection{LDAP fields storing credentials.}

For this reason, the OpenLDAP documentation recommends storing passwords in a hashed format \cite{} . There are the following storage scheme for the LDAP attribute \texttt{userpassword}:

\begin{itemize}
    \item \textbf{SSHA Password Storage Scheme:} The SSHA (Salted SHA) password storage scheme is a salted version of the SHA algorithm and is considered one of the most secure methods. It adds a unique salt to each password before hashing, enhancing security against precomputed rainbow table attacks. For example, the following values represent the same password in different salted forms: 

    \begin{verbatim}
    {SSHA}DkMTwBl+a/3DQTxCYEApdUtNXGgdUac3
    {SSHA}d0Q0626PSH9VUld7yWpR0k6BlpQmtczb
    \end{verbatim}
    
    \item \textbf{CRYPT Password Storage Scheme:} This scheme leverages the operating system's \texttt{crypt(3)} hash function, capable of supporting a variety of hashing algorithms. The resultant hashed value is prefixed with a dollar sign and an identifier (\$<id>), where <id> denotes the specific hashing algorithm used—'1' for MD5, '8' for PBKDF2, and so on. For instance, a \texttt{userPassword} attribute's crypt value could appear as follows:

    \begin{verbatim}
    {CRYPT}$1$czBJdDqS$TmkzUAb836oMxg/BmIwN.1
    \end{verbatim}

    \item \textbf{MD5 Password Storage Scheme:} Hashing the password using the MD5 algorithm is widely regarded as insecure in modern cryptographic practices.

    \item \textbf{SMD5 Password Storage Scheme:} This scheme represents an advancement over the standard MD5 algorithm by incorporating salt into the hashing process. This addition results in the potential for multiple unique hash representations for the same password. Example representations are as follows:

    \begin{verbatim}
    {SMD5}4QWGWZpj9GCmfuqEvm8HtZhZS6E=
    {SMD5}g2/J/7D5EO6+oPdklp5p8YtNFk4=
    \end{verbatim}
    
\end{itemize}

During our subsequent evaluations, we successfully discerned additional categories represented within fields that store passwords or credentials in any form, which include: Censored values, NTLM and LM Hashes, Base64 encoded values, and many more (see also Table \ref{tab:Password leaks on LDAP Servers.}). The most shocking discovery, however, was the presence of plaintext passwords. These were not limited to isolated instances or confined to smaller test servers. Alarmingly, plaintext passwords were found on servers handling several thousand users, including those owned by major international corporations, universities and government entities. This highlights a significant oversight in security protocols across various high-profile organizations. But why are the passwords publicly accessible at all? 

The critical question arises: Why are these passwords publicly accessible in the first place? In discussions with an LDAP administrators, it emerged that the standard practice is to restrict access to a user's password solely to that individual user. However, this practice is not standardized, and as a result, our internet scans revealed a disturbing prevalence of misconfigurations, where passwords have been accesible. We detail these findings and their implications in this chapter.

As highlighted in Table \ref{tab:Most common attributes on servers.}, we observed that certain servers populate attributes (e.g., \texttt{userpassword}) that suggest that secrets, such as clear text passwords, are stored in them and that they are publicly accessible without any kind of authentication. To get to the bottom of this suspicion, we closely examined all attributes that were replicated on multiple servers. This involved creating three lists, which were then methodically cross-checked. This process resulted in a list of LDAP fields used to store credentials (see Table \ref{tab:Secret leaking attributes on servers.}). By subsequently analyzing our dataset, we were able to identify 1644 servers potentially publish secrets. For b servers (b\%) the leak was identified within the samples, and for c servers (c\% ) a leak was identified within the admin accounts found.

Another critical issue is that the limitations of these servers, as described in Chapter X, can be circumvented. This allows for the possibility of extracting a complete set of user passwords. The consequences of such actions can be severe and are discussed in detail in Chapter Y. This highlights the urgent need for more robust security measures to prevent unauthorized access and data breaches.

\begin{table}[htbp]
\begin{tabularx}{0.5\textwidth}{|l|X|}
\hline
\textbf{Attribute} & \textbf{Count} \\ {Leaked Passwords}
\hline
\hline
userPassword & 1375 \\ 
sambaNTPassword & 231 \\ \todo{group NT and LM Password Hashes}
sambaLMPassword & 203 \\
password & 81 \\
goImapPassword & 11 \\
clearPassword & 8 \\
krbPrincipalKey & 3 \\
ntPassword & 3 \\
lmPassword & 1 \\
LMPassword & 1 \\
NTPassword & 1 \\
\hline
\end{tabularx}
\caption{Secret leaking attributes on servers.}
\label{tab:Secret leaking attributes on servers.}
\end{table}

\todo{Update the following paragraph:}

However, due to the nature of our random sampling method, there is a possibility that a server might leak secrets which we might not detect, as our sample may not be affected by the data leak. Consequently, we decided to conduct a more targeted search for servers that disclose authentication information. For this purpose, we utilized our list of attributes (refer to Table \ref{tab:Secret leaking attributes on servers.}) and requested server samples with a filter based on these attributes. This approach enabled us to identify a total of 'Y' servers in a second round, which is an increase of y\% compared to our initial findings.

\subsection{Passwort Types and Classification}

\subsubsection{OpenLDAP Password Standard}
https://www.openldap.org/doc/admin24/security.html
userPassword - openldap default

14.4.1. SSHA password storage scheme

14.4.2. CRYPT password storage scheme

14.4.3. MD5 password storage scheme

14.4.4. SMD5 password storage scheme

14.4.5. SHA password storage scheme

14.4.6. SASL password storage scheme

\subsubsection{LM, NT, NTLM Hashes}

In an LDAP server, if there are both an NT password hash and an LM (LAN Manager) password hash, they are indeed two different things, not a combined NTLM password hash.

Here's a brief explanation of each:

NT Password Hash: This is a hash used by more modern versions of Windows (starting with Windows NT). It's more secure than the LM hash and is generated using the MD4 hashing algorithm applied to the Unicode (UTF-16LE) representation of the password.

LM Password Hash: This is an older and less secure hash format used by legacy systems (like Windows 95/98 and early versions of Windows NT). LM hashes are notorious for being weak: they convert the password to uppercase, pad it to 14 characters, split it into two 7-character halves, and hash each half with the DES algorithm.

NTLM: NTLM (NT LAN Manager) is an authentication protocol that can use either of these hash types for authentication, depending on the system and configuration. NTLM is a term that refers to the suite of protocols that replaced the original LAN Manager authentication. NTLMv1 primarily used LM hashes, while NTLMv2, which is more secure, uses NT hashes.

In LDAP directories, particularly those integrated with Windows systems or Samba, you may find attributes like sambaNTPassword and sambaLMPassword to store these hashes. This is for compatibility with different versions of Windows clients and servers.

\subsubsection{SHA Hashes}

\subsubsection{wildcards}

....

\subsubsection{Password Fields}

As highlighted in Table \ref{tab:Most common attributes on servers.}, we observed that certain servers populate attributes that suggest that secrets, such as user passwords, are stored in them. To get to the bottom of this suspicion, we closely examined all attributes that were replicated on multiple servers. This involved creating three lists, which were then methodically cross-checked. This process resulted in a list of LDAP fields used to store credentials (see Table \ref{tab:Secret leaking attributes on servers.}). By subsequently analyzing our dataset, we were able to identify 1644 servers potentially publish secrets. For b servers (b\%) the leak was identified within the samples, and for c servers (c\% ) a leak was identified within the admin accounts found.




\subsection{Password Evaluation}

After identifying that some servers populate fields suggesting the storage of credentials, the question arose regarding the nature of the published values: whether they are plaintext passwords, hashes, or perhaps entirely redacted.

To assess this, we created a view in our database of the servers with password samples and examined these samples in detail. For this purpose, we developed a Python script, \texttt{pwd\_evaluators.py}, which automatically analyzes the fields and categorizes the values into different classes. The script processes the data step by step as follows:

\begin{enumerate}
    \item Identification of redacted passwords: Some passwords are indeed censored, meaning their actual value remains undisclosed. The redaction typically appears as: \lstinline{********} or \lstinline{#########}.
    \item Identification of NTLM hashes: The field names were significantly useful for identifying these values. Random sampling demonstrated that certain fields, such as \texttt{sambalmpassword} and \texttt{sambantpassword}, contain NTLM hashes.
    \item Identification by tag: Many hash values can be identified by their tag. For instance, according to OpenLDAP documentation, passwords are stored in the format \lstinline|{TAG}|Value. The various tags are described in section x.y.z.
    \item Identification of potential hash values: Certain hash formats, like BCRYPT or MD5, have specific characteristics. For example, the BCRYPT format has a rather distinct pattern, and an MD5 hash always has a fixed length of 32 bytes.
    \item Identification of encoded values: Recognizable again by patterns. For example, due to padding, 2/3 of Base64 encoded values end with one or two '=' characters. Decoding is tentatively performed, and the result or error is analyzed to determine if it represents an encoded value. Some values also explicitly indicate their encoding method.
\end{enumerate}

This procedure significantly reduced the number of values. However, a set of x values remained. These were then manually evaluated, revealing that the remaining passwords are in plaintext.

In total, Y servers were found populating password fields, and the described detailed analysis of the values from these servers is presented in Table X. The table indicates that out of 1639 servers, 835 (51\%) are transmitting credentials in an insecure format.

\begin{table}
\begin{center}
\begin{tabularx}{0.45\textwidth}{|l|r|X|}
\hline
\textbf{Type} & \textbf{Count} & \textbf{Ratio} \\
\hline
\hline
CENSORED & 731 & 44.60\% \\
Plaintext & 449 & 27.39\% \\
SSHA1 & 320 & 19.52\% \\
NTLM & 231 & 14.09\% \\
SHA1 & 197 & 12.02\% \\
MD5 & 189 & 11.53\% \\
LM & 180 & 10.98\% \\
CRYPT\_CLASSIC & 85 & 5.19\% \\
SMD5 & 82 & 5.00\% \\
SHA-\{256,512\} & 54 & 3.29\% \\
Others & 29 & 1.77\% \\
BCRYPT & 25 & 1.53\% \\
SSHA-\{256,512\} & 24 & 1.46\% \\
CRYPT\_UNIDENTIFIED & 4 & 0.24\% \\
KERBEROS & 1 & 0.06\% \\
YESCRYPT & 1 & 0.06\% \\
PBKDF2-\{256,512\} & 1 & 0.06\% \\
\hline
\end{tabularx}
\end{center}
\caption{Password leaks on LDAP Servers.}
\label{tab:Password leaks on LDAP Servers.}
\end{table}

\subsubsection{Top 20 Leaks}


\begin{table*}[!ht]
\centering
\begin{tabular}{|c|c|c|c|c|}
 \hline
 \textbf{Company} & \textbf{Country} & \textbf{City} & \textbf{Count} & \textbf{Types}\\ 
 \hline
 \hline
 unknown & CN & Beijing & 245272 & NTLM, CENSORED \\
 \hline
 unknown & CN & Beijing & 245214 & NTLM, CENSORED \\
 \hline
 unknown & US & Denver & 214141 & Plaintext \\
 \hline
 Microsoft Corporation & US & Des Moines & 176933 & SHA \\
 \hline
 DigitalOcean, LLC & DE & Frankfurt am Main & 161317 & MD5, SSHA \\
 \hline
 Security Data & EC & Azogues & 124708 & SSHA \\
 \hline
 unknown & EC & Azogues & 90778 & SSHA \\
 \hline
 unknown & GH & Accra & 86090 & NTLM, SHA, LM, Plaintext, SSHA, CRYPT \\
 \hline
 unknown & CA & Toronto & 83169 & MD5 \\
 \hline
 unknown & US & Baxter Springs & 82869 & CENSORED, Plaintext, CRYPT \\
 \hline
 unknown & US & North Charleston & 72116 & Plaintext \\
 \hline
 unknown & TH & Bangkok & 66679 & SHA \\
 \hline
 unknown & BA & Mostar & 66582 & SHA \\
 \hline
 unknown & TN & Ariana & 51309 & Plaintext \\
 \hline
 Makerere University & UG & Kampala & 46566 & NTLM, LM, CENSORED \\
 \hline
 unknown & VN & Hanoi & 46314 & MD5, Plaintext \\
 \hline
 unknown & TN & Tunis & 45942 & Plaintext \\
 \hline
 unknown & JP & Inzai & 35609 & NTLM, LM, CENSORED, CRYPT \\
 \hline
 unknown & JP & Fukuoka & 35609 & NTLM, LM, CENSORED, CRYPT \\
 \hline
 unknown & EC & Loja & 35212 & SHA, Plaintext \\
 \hline
\end{tabular}
\end{table*}

\begin{table*}[!ht]
\resizebox{\textwidth}{!}{
\centering
\begin{tabular}{|c|c|c|c|c|c|}
 \hline
\textbf{Length} & \textbf{Numbers Only} & \textbf{Lowercase} & \textbf{Upper- and Lowercase} & \textbf{Numbers and Letters} & \textbf{Numbers, Letters, and Symbols}\\ 
 \hline
 \hline
 < 4 & 581 & 216 & 3 & 5 & 7\\
 \hline
 4 & 154 & 158 & 2 & 71 & 135\\
 \hline
 5 & 156 & 114 & 13 & 108 & 39\\
 \hline
 6 & 4760 & 262 & 8 & 500 & 75\\
 \hline
 7 & 150 & 214 & 27 & 484 & 1916\\
 \hline
 8 & 1199 & 269 & 598 & 6434 & 1210\\
 \hline
 9 & 3162 & 144 & 14 & 3734 & 894\\
 \hline
 10 & 288 & 130 & 149 & 4110 & 1359\\
 \hline
 11 & 23 & 66 & 5 & 8371 & 330\\
 \hline
 12 & 4 & 43 & 14 & 981 & 625\\
 \hline
 13 & 1234 & 31 & 0 & 270 & 281\\
 \hline
 14 & 2 & 23 & 2 & 161 & 142\\
 \hline
 > 14 & 48 & 51 & 10 & 694 & 1088\\
 \hline
\end{tabular}
}
\end{table*}

\subsection{Analysis of Password Entropy in LDAP Servers}



\subsubsection{clear text passwords}

////
Warum ist jede Form davon schlecht, außer evtl die wildcards?
password sicherheit ist ein problem, auch hashes sind nicht sicher, wenn die nutzer nicht sichere passwörter wählen und das sie das nicht tun ist ein bekanntes problem, d.h. es ist davon auszugehen, dass einige dieser passwörter durch z.B. mimikatz crackstation diese zu cracken -> es sollten keine password hashes frei und öffentlich ins netz gestellt werden
außerdem, sobald es einmal geleakt ist, studie x zeigt, dass user ihre passwörter immer wieder und wieder verwenden
////

--> Classification

--> List: Server X Has ABC.ABC Passwords of Type Z (Counter)

--> Disclousure



\begin{landscape}
\begin{table}[phtb]
\footnotesize
    \centering
    \begin{tabular}{lrrrrrrrrrrrrrrrrrrr}
         \hline
                 \multirow{2}{*}{Country}&\multicolumn{2}{c}{Passwords}                    && \multicolumn{3}{c}{PII} && \multicolumn{3}{c}{Authentication} && \multicolumn{2}{c}{Sensitive Config} &\multirow{2}{*}{Vulnerable} \\
                 \cline{2-3}\cline{5-7} \cline{9-11}\cline{13-14}
         & Plain & Hashed && Proper TLS & Invalid Chain & Weak TLS && Proper TLS & Invalid Chain & Weak TLS && DICOM & Sieve &&\\
         \hline
         World & 5000 (5\%) & 1000 (1\%) && 2000 (20\%) & 1000 (10\%)& 1000 (10\%)&&2000 (20\%) & 1000 (10\%)& 1000 (10\%) && 1000 (10\%)\\
         US \\
         Germany\\
         \hline
    \end{tabular}
    \caption{Caption}
    \label{tab:my_label}
\end{table}

% Table moved to actual paper ;-)
\end{landscape}
\end{document}