\chapter*{Publications by the Author}
\label{sec:publications}

Below is a list of peer-reviewed academic publications that the author has authored or co-authored in chronological order:

\begin{itemize}
    \item J. Kaspereit, G. Öndarö, G. L. Cesar, S. Ebbers, F. Ising, C. Saatjohann, M. Jonker, R. Holz, and S. Schinzel, ``LanDscAPe: Exploring LDAP weaknesses and data leaks at internet scale,'' in 33rd USENIX Security Symposium (USENIX Security 24). Philadelphia, PA: USENIX Association, Aug. 2024, pp. 1225-1242. [Online]. Available: \url{https://www.usenix.org/conference/usenixsecurity24/presentation/kaspereit}

    \item G. L. Cesar, G. Öndarö, J. Kaspereit, F. Ising, S. Schinzel, M. Jonker, and R. Holz, ``Characterizing hosting and security practices for public-facing ldap servers,'' in 2025 21st International Conference on Network and Service Management (CNSM), 2025, pp. 1-9.

    \item G. L. Cesar, R. Holz, and M. Jonker, ``TODO: longitudinal analysis of dmarc across country code top-level domains,'' in NOMS, 2026, pp. 1-11.

    \item R. Hendriks and G. L. Cesar \ldots , ``TODO: a deep dive on deployment strategies of services provisioned using anycast,'' 2026, pp. 1-11.

\end{itemize}

Below is a list of non-peer-reviewed \dataset publications that the author has authored or co-authored that support the reproducibility of the academic publications, in chronological order:

\begin{itemize}
    \item Luvizotto Cesar, G., Öndarö, G., Kaspereit, J., Ising, F., Schinzel, S., Jonker, M., and Holz, R. (2025). Characterizing Hosting and Security Practices for Public-Facing LDAP Servers [Data set]. 21st International Conference on Network and Service Management (CNSM), Bologna, Italy. Zenodo. \url{https://doi.org/10.5281/zenodo.17019740}.

    \item Luvizotto Cesar, G., R. Holz, and M. Jonker (2026). TODO: longitudinal analysis of dmarc across country code top-level domains [Data set]. NOMS, Rome, Italy. Zenodo. \url{https://doi.org/TODO}.

    %\item Hendriks, R., and G. L. Cesar (2026). TODO: a deep dive on deployment strategies of services provisioned using anycast [Data set]. Place, Country. Zenodo. \url{https://doi.org/TODO}
\end{itemize}
