% !TEX root = ../main.tex
\section{Background and Related Work}
\mypara{Background}
\label{sec:background}
\acrshort{LDAP} is a client-server protocol to facilitate transfer and access of data stored in directory services such as OpenLDAP or \acrfull{AD}.
We use the generic term \textit{\gls{LDAP} servers} to refer to all servers that speak the protocol and distinguish by directory service as needed. Connection-less \gls{LDAP} over UDP is restricted to a small set of queries; hence we do not investigate it. \gls{LDAP} typically runs over TCP on port 389 (clear text with optional \starttls) or 636 (implicit \gls{TLS}), while ports 3268 (clear text/\starttls) and 3269 (implicit \gls{TLS}) are reserved for the \gls{GC} service in Microsoft’s \gls{AD}. The \gls{GC} is an \gls{AD} role to manage and access copies of data items across a multitude of \gls{LDAP} servers~\cite{alvinashcraft_GlobalCatalogWin32_2020}. \gls{LDAP} stores data in a tree-like hierarchy. The special Root \gls{DSE} data entry stores information about the server's functionality in form of attributes and it can help identify the \gls{LDAP} product. \gls{LDAP} may use \gls{TLS}, where a cipher suite is agreed upon and a chain of X.509 certificates is sent to a client. RFC-9325 gives best-practice recommendations.

%\gls{LDAP} may use \gls{TLS} when used with TCP. Presently, only the most recent versions \gls{TLS} 1.3 and 1.2 are still considered secure, with \gls{TLS} 1.3 being the considerably stronger standard. RFC 9325 gives best-practice recommendations, including on the use of cipher suites~\cite{rfc9325}. During the \gls{TLS} handshake, client and server agree on a cipher suite, with the server picking from a list offered by the client. The server sends a chain of X.509 certificates to authenticate. Certificates are valid for a specified period, which serves to limit the attack window in the event of a compromised certificate. 

A certificate chain must be anchored at a trusted root, requiring the \gls{LDAP} client to be configured with the required root certificate(s). The so-called end-host (or leaf) certificate provides a cryptographic binding of an identifier---typically the domain name of the \gls{LDAP} server---to a corresponding public key.
On the Web, public \glspl{CA} issue certificates under CA/Browser Forum rules (\eg verification of domain ownership), and root stores are managed by OS (\eg Windows, macOS, and Linux) and browser vendors (\eg Firefox).
For \gls{LDAP}, no comparable body or standardization efforts exist. In many cases (\eg Linux, Windows), the root store that the \gls{LDAP} client relies on is the same as for the Web. In refined setups, the \gls{LDAP} server administrator may supply it directly, even using a private \gls{CA} to issue their own certificates. In this case, the administrators must also deploy the root certificate to their \gls{LDAP} clients using tools like \gls{AD} Certificate Services or scripts. In such a \textit{private PKI}, one should issue intermediate certificates from the root certificate, which in turn are used to issue a leaf certificate. This setup is important as it allows the private key for the root certificate to be kept in a secure location. An alternative, semi-private PKI setup is also possible: an operator could request a sub-CA certificate from a public CA, \ie an intermediate certificate, from which they then issue their own certificates. This setup must be tightly controlled so leaf certificates are only ever issued for domains under control of the administrator~\cite{cabr}.
% https://cabforum.org/working-groups/server/baseline-requirements/requirements/ 3.2.2.4.4

A discouraged practice is to deploy so-called self-signed certificates, where the key used to sign a certificate is also the certified key. In such a case, the client must be pre-configured to accept only this certificate---or users told to ignore the warnings their \gls{LDAP} client would show. The setup is only suitable if the \gls{LDAP} server serves a minimal set of users. It also constitutes a security risk as the private key remains online in memory.  As certificates are available for free and can be relatively easily deployed with the ACME protocol, there is little justification to use self-signed certificates any more.

\input{src/relatedwork}
