% !TEX root = main.tex
\begin{abstract}
    % *** intro: what is anycast, why is it important
    IP anycast is a fundamental Internet technology where a prefix is made available in multiple locations
    to bring services closer to users
    and, most importantly, improve service resilience.
    % *** problem statement: why do we do our study
    Despite the growth in anycast---with censuses reporting \textbf{\num{1e3}} ASes and \textbf{\num{14e3}} /24-prefixes in 2026---
    little is known about how operators provision services using anycast.
    % *** proposed solution: what do we do to address the gap
    We address this gap
    by characterizing the deployment strategies used by anycast operators,
    based on the locations behind anycast prefixes
    and the topologies visible in routing data.
    %
    We design a pipeline that measures 120 ports on TCP and UDP, and evaluates the use of QUIC
    and 32 different application-layer protocols to identify services replicated using anycast.

    % *** main takeaways of findings
    We show large differences in deployment strategies:
    77\% of anycast Autonomous Systems (ASes)
    announce prefixes with a few IP addresses hosting services,
    whereas 7\% fully utilize their prefixes,
    with five ASes alone accounting for more than 88\% of anycast IP addresses hosting services.
    %
    We find 18\% of ASes make use of the same \gls{byoip} infrastructure hosting provider,
    highlighting hidden dependencies not visible without topological analysis.
    %
    Regional anycast is widespread,
    with 35\% of operators replicating prefixes within a single continent,
    including 23 ASes with regional prefixes in multiple regions.
    %
    While most anycast prefixes are used for web services (including deployments with significant QUIC adoption),
    they are largely originated by a few \gls{cdn} ASes.
    Conversely, we find most ASes use anycast to replicate DNS using a few prefixes,
    highlighting distinct strategies between \glspl{cdn} and DNS operators.
\end{abstract}

\iffalse
\begin{IEEEkeywords}
Resilience, Internet Services, Anycast
\end{IEEEkeywords}
\fi
